Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid

### 2022-06-14 05_Presentation/aiddata_presentation.tex
AidData conference presentation

%% Load the markdown package
\usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}
%%begin novalidate
\markdownSetup{rendererPrototypes={
 link = {\href{#2}{#1}},
 headingOne = {\section{#1}},
 headingTwo = {\subsection{#1}},
 headingThree = {\begin{frame}\frametitle{#1}},
 headingFour = {\begin{block}{#1}},
 horizontalRule = {\end{block}}
}}

@@

\title{Friends Get More Money, Attention and Handshakes:
Chinese Foreign Aid, Xinhua and Diplomatic Visits}

\author{Lucie Lu, Miles D. Williams\\ University of Illinois at Urbana-Champaign}
\date {MPSA 2022 \\ April 8, 2022}

@@

\begin{itemize}
    \item China seems to deliberately keep its foreign aid giving a secret.
    \item However, development finace arguably should promote "South-South cooperation" and improve China's image abroad.
    \item \textit{Such goals require transparency, so what should we make of its absence?}
\end{itemize}

@@

\begin{itemize}
\item \textbf{The Puzzle}: \textit{Absent formal modes of transparency, what evidence do we have that Chinese aid serves public diplomacy?}
\item \textbf{Argument}: \textit{We should observe complementarties between where China sends a greater number of diplomatic missions and that receive greater media coverage in outlets targeted at foreign audiences with where China gives greater foreign aid.}
\end{itemize}

@@

Two dimensions of Chinese public diplomacy efforts:

\begin{itemize}
    \item State-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

@@

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} aid.

>>>>

%% Load the markdown package
\usepackage[footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,hybrid]{markdown}
%%begin novalidate
\markdownSetup{rendererPrototypes={
 link = {\href{#2}{#1}},
 headingOne = {\section{#1}},
 headingTwo = {\subsection{#1}},
 headingThree = {\begin{frame}\frametitle{#1}},
 headingFour = {\begin{block}{#1}},
 horizontalRule = {\end{block}}
}}

@@

\title{Friends Get More Money, Attention, and Handshakes:
Xinhua, Diplomacy, and Chinese Foreign Aid}

\author{Lucie Lu, Miles D. Williams \\ University of Illinois at Urbana-Champaign}
\date {AidData Academic Roundtable \\ June 24, 2022}

@@

\includegraphics[width=\linewidth]{china_aid_logo.jpg}

\includegraphics[width=\linewidth]{low_transparency.jpeg}

@@

\textbf{The Puzzle}: \textit{Absent traditional modes of transparency, how does Beijing leverage its international development finance in service of its diplomatic and legitimacy-seeking objectives?}

\textbf{Our Answer}: \textit{China complements other} \textbf{visible} \textit{foreign policy activities with greater development finance.}

\begin{itemize}
  \item AidData's \textit{China's Public Diplomacy Dashboard}
  \item Cline Center for Advanced Social Research's \textit{Global News Index and Extracted Features Repository}
\end{itemize}

@@

Two dimensions of Beijing's public diplomacy:

\begin{itemize}
    \item China’s bilateral South-South diplomatic activities.
    \item State-sponsored \textit{Xinhua} media coverage of developing countries intended for foreign audiences.

@@
